\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-08-02 jss/article.tex
up to In Figure 6 the 95% interval plot

         obs.mean  n   X1 prior.mean shrinkage low.intv post.mean upp.intv post.sd
1           0.400 45 1.00      0.310     0.715    0.248     0.335    0.429   0.046
2           0.378 45 1.00      0.310     0.715    0.244     0.329    0.420   0.045
3           0.356 45 1.00      0.310     0.715    0.240     0.323    0.411   0.044
4           0.333 45 1.00      0.310     0.715    0.236     0.316    0.403   0.043
5           0.311 45 1.00      0.310     0.715    0.230     0.310    0.396   0.042
6           0.311 45 0.00      0.233     0.715    0.179     0.256    0.341   0.041
7           0.289 45 0.00      0.233     0.715    0.175     0.249    0.331   0.040
8           0.267 45 0.00      0.233     0.715    0.171     0.243    0.323   0.039
9           0.244 45 0.00      0.233     0.715    0.166     0.237    0.315   0.038
10          0.244 45 1.00      0.310     0.715    0.210     0.291    0.379   0.043
11          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308   0.038
12          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308   0.038
13          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308   0.038
14          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375   0.044
15          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375   0.044
16          0.200 45 0.00      0.233     0.715    0.155     0.224    0.302   0.038
17          0.178 45 0.00      0.233     0.715    0.148     0.218    0.297   0.038
18          0.156 45 0.00      0.233     0.715    0.140     0.211    0.292   0.039
colMeans    0.265 45 0.44      0.267     0.715    0.191     0.267    0.351   0.041
\end{CodeOutput}
\end{CodeChunk}
Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233. Also note that shrinkage estimates are the same for all players. It makes sense because shrinkage ($B_{j}\equiv r / (r+n_{j})$) is determined solely by the relative amount of information between the first-level and the second-level hierarchies. The fact that all players have the same amount of observed information ($n_{j}=45$) and $\hat{r}=\textrm{exp}(4.727)=113$ from below summary tell why the estimated shrinkage is 0.715 (=113 / (113 + 45)).

@@

The below summary includes the result of logistic regression fit because we did not know prior means in advance. We had to estimate them via this logistic regression model. Let's look at the p-value of the indicator covariate. It shows that the two prior means distinguishing outfielders from other positions were significantly different (p-value = 0.038), supporting our initial belief. The positive sign of $\hat{\beta}_{1}$ indicates that the mean batting average for all the outfielders tends to be higher than that for those in the other positions.

\begin{CodeChunk}
\begin{CodeInput}
R> summary(b)
\end{CodeInput}
\begin{CodeOutput}
Main summary:

@@

>>>>

         obs.mean  n   X1 prior.mean shrinkage low.intv post.mean upp.intv post.sd
1           0.400 45 1.00      0.310     0.715    0.248     0.335    0.429   0.046
2           0.378 45 1.00      0.310     0.715    0.244     0.329    0.420   0.045
3           0.356 45 1.00      0.310     0.715    0.240     0.323    0.411   0.044
4           0.333 45 1.00      0.310     0.715    0.236     0.316    0.403   0.043
5           0.311 45 1.00      0.310     0.715    0.230     0.310    0.396   0.042
6           0.311 45 0.00      0.233     0.715    0.179     0.256    0.341   0.041
7           0.289 45 0.00      0.233     0.715    0.175     0.249    0.331   0.040
8           0.267 45 0.00      0.233     0.715    0.171     0.243    0.323   0.039
9           0.244 45 0.00      0.233     0.715    0.166     0.237    0.315   0.038
10          0.244 45 1.00      0.310     0.715    0.210     0.291    0.379   0.043
11          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308   0.038
12          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308   0.038
13          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308   0.038
14          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375   0.044
15          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375   0.044
16          0.200 45 0.00      0.233     0.715    0.155     0.224    0.302   0.038
17          0.178 45 0.00      0.233     0.715    0.148     0.218    0.297   0.038
18          0.156 45 0.00      0.233     0.715    0.140     0.211    0.292   0.039
colMeans    0.265 45 0.44      0.267     0.715    0.191     0.267    0.351   0.041
\end{CodeOutput}
\end{CodeChunk}
Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233. Also note that the shrinkage estimates are the same for all players due to the fact that they are determined solely by the relative amount of information between the first-level and the second-level hierarchies, ($B_{j}\equiv r / (r+n_{j})$ = $\equiv exp(4.727) / (exp(4.727)+45)$ = 0.715).

@@

In problems where a covariate is present \code{gbp} provides a regression summary (in this example logistic regression)
\begin{CodeChunk}
\begin{CodeInput}
R> summary(b)
\end{CodeInput}
\begin{CodeOutput}
Main summary:

@@

We see that the two prior means distinguishing outfielders from other positions were significantly different (p-value = 0.038), supporting our initial belief. The positive sign of $\hat{\beta}_{1}$ indicates that the mean batting average for all the outfielders tends to be higher than that for those in the other positions.
